---
title: "India at Summer Olympics"
subtitle: "TidyTuesday 8/6/24"
author: "Havisha Khurana"
output: 
    html_document:
        theme: journal
        toc: yes
        toc_float: 
            collapsed: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      error = FALSE)
```

```{r}
library(tidyverse)
library(rvest)
library(showtext)
```

```{r}
font_add_google(name = "Open Sans", family = "Open Sans")
showtext_auto()
```


```{r}
olympics <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-08-06/olympics.csv')
```

```{r}
# from 1900-2016
ind_olympics <- olympics %>%
    filter(team %in% c("India", "India-1","India-2"))

```


```{r}
#from wikipedia
tokyo20_representation <- read_html("https://en.wikipedia.org/wiki/India_at_the_2020_Summer_Olympics#cite_note-List-6") %>%
    html_elements("table") %>%
    .[2] %>%
    html_table() %>%
    .[[1]] %>%
    janitor::clean_names() %>%
    mutate(year = 2021,
        game = "2021 Tokyo",
        representation = total) %>%
    filter(sport != "Total")

tokyo20_medals <- read_html("https://en.wikipedia.org/wiki/India_at_the_2020_Summer_Olympics#cite_note-List-6") %>%
    html_elements("table") %>%
    .[4] %>%
    html_table() %>%
    .[[1]] %>%
    janitor::clean_names() %>%
    mutate(year = 2021,
           medals = total,
           game = "2021 Tokyo")

tokyo_df <- tokyo20_representation %>%
    left_join(tokyo20_medals %>% select(sport, medals)) %>%
    mutate(medals = ifelse(is.na(medals), 0, medals),
           sport = case_when(
               sport == "Table tennis" ~ "Table Tennis",
               sport == "Field hockey" ~ "Hockey",
               sport == "Equestrian" ~ "Equestrianism",
               TRUE ~ sport)) 
```

```{r}
paris24_representation <- read_html("https://en.wikipedia.org/wiki/India_at_the_2024_Summer_Olympics") %>%
    html_elements("table") %>%
    .[8] %>%
    html_table() %>%
    .[[1]] %>%
    janitor::clean_names() %>%
    mutate(year = 2024,
           game = "2024 Paris",
           representation = athletes, medals = NA,
           sport = gsub("(.*)(\\[a\\])", "\\1", sport),
           sport = case_when(
               sport == "Table tennis" ~ "Table Tennis",
               sport == "Field hockey" ~ "Hockey",
               sport == "Equestrian" ~ "Equestrianism",
               TRUE ~ sport)) %>%
    filter(sport != "Total")
```

```{r}
logo_path <- here::here("images/ioc_logo_wo_rings.png")
```


```{r}
year_sport_n <- ind_olympics |>
    filter(season == "Summer") |>
    select(id, name, sex, year, sport, city) |>
    distinct() |>
    group_by(year, sport) |>
    summarize(representation = n(),
              game = paste(year, city)) |>
    distinct()

plot1_df <- year_sport_n %>%
    rbind(tokyo_df) %>%
    rbind(paris24_representation) %>%
    group_by(year) %>%
    mutate(total = sum(representation, na.rm = T)) %>%
    ungroup() %>%
    mutate(representation = case_when(
        representation < 2 ~ as.character(representation),
        representation < 6 ~ "2-5",
        representation < 11 ~ "6-10",
        representation < 21 ~ "11-20",
        representation > 20 ~ ">20"
    ),
    representation = factor(representation, levels = c("1","2-5","6-10","11-20",">20")))
```

```{r}
ind_independence <- tibble(
    year = 1947,
    game = "1948 London"
)
```

## It's Olympics Time!

This week, for TidyTuesday, I'm exploring Olympics data from 1896-2024. Particularly, I'm interested in exploring **India's** representation in the Olympics over time. I used the TidyTuesday data for data until 2016 and then scraped data for 2021 and 2024 Summer Olympics.

-   First participated: 1900 as *British-India*
-   First participated as an **Independent Country** in 1948

### How many representatives, events, and medals?


```{r}
year_total_medal_sports <- ind_olympics |>
  filter(season == "Summer") |>
  #group_by(year, event) |>
  # mutate(medals = ifelse(sum(!is.na(medal), na.rm = T) == 0,
  #                        0,
  #                        length(unique(medal)))
  #        )|>
  group_by(year) |>
  summarize(
    representatives_n = length(unique(id)),
    sport_n = length(unique(sport)),
    event_n = length(unique(event)),
    medals_n = length(unique(event[!is.na(medal)])),
    game = paste(year, city)
  ) |>
  distinct()

tokyo_df_total <- tokyo_df |>
  summarize(
    year = year,
    game = game,
    representatives_n = sum(representation),
    sport_n = n(),
    event_n = NA,
    medals_n = sum(medals)
  ) |>
  distinct()

paris_df_total <- paris24_representation |>
  summarize(
    year = year,
    game = game,
    representatives_n = sum(representation),
    sport_n = n(),
    event_n = NA,
    medals_n = NA
  ) |>
  distinct()

plot3_df <- year_total_medal_sports |>
  rbind(tokyo_df_total) |>
  rbind(paris_df_total)
```


```{r fig.height = 8, fig.width = 10}
plot3 <- ggplot(plot3_df) +
  geom_line(aes(x = year, y = representatives_n), color = "#138808", linewidth  = 1) +
  geom_line(aes(x = year, y = sport_n*4), color = "#FF9933", linewidth = 1) +
  geom_line(aes(x = year, y = medals_n*4), color = "#FF9933",linewidth = 1, linetype = 3)+
  geom_vline(xintercept = 1947, color  = "#06038D", linetype = 2) + #India independence
  scale_y_continuous(
    
    # Features of the first axis
    name = "# Representatives",
    breaks = seq(0,120, 20),
    # Add a second axis and specify its features
    sec.axis = sec_axis( trans=~./4, name="# Sports/Medals")
  ) +
  scale_x_continuous(
    breaks = plot3_df$year,
    labels = plot3_df$game,
  ) + 
  labs(
    x = "",
    caption = "Source: RGriffin Olympic Dataset for 1900-2016, and Wikipedia for 2021 and 2024.\nTotal includes representatives who participated, doesn't include representatives on reserve for 2024",
    title = paste0("Representation, Sports, and Medals<br>for the ,<img src = '", logo_path,"' height = 18> Summer Olympics Contingent")
  )+
     annotate(
    geom = "label", 
    x = 1945, 
    y = 86,
    label = "Became Independent",
    color = "#06038D",
    size = 8
  ) +
  annotate(
    geom = "line", 
    x = c(1958,1965), 
    y = c(110,110),
    linetype = 1,
    color = "#FF9933",
    linewidth = 0.75
  ) +
  annotate(
    geom = "line", 
    x = c(1958,1965), 
    y = c(100,100),
    linetype = 3,
    color = "#FF9933",
    linewidth = 0.75
  ) +
    annotate(
    geom = "text", 
    x =1975, 
    y = 110,
    label = ":# Sports",
    color = "#FF9933",
    size = 10
  ) +
  annotate(
    geom = "text", 
    x = 1975, 
    y = 100,
    label = ":# Medals",
    color = "#FF9933",
    size = 10
  ) +
  theme_minimal(32)+
  theme(
     axis.title.y = element_text(color = "#138808", size=26),
    axis.title.y.right = element_text(color = "#FF9933", size=26),
     text = element_text(family = "Open Sans"),
        plot.title = ggtext::element_markdown(hjust =0.5, face = "bold", lineheight = 0.25),
        axis.text.x = element_text(angle = 60, hjust = 0.95, color = "gray40",
                                   size = 26),
        plot.caption = element_text(color = "gray40", size = 24, lineheight = 0.5),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(color = "azure2", linewidth = 0.2),
        legend.position = "right"
  )

plot3
#ggsave("overview.jpeg", plot3, height = 6, width = 8)
```

- **Pre-Independence Era**: Indian contingent had around 20 representatives competing in fewer than 5 sports.
  
- **1948 London Olympics**: First Olympics after India's independence with about 80 representatives in 10 sports.

- **Fluctuations**: Number of representatives and sports fluctuated since 1948, with the lowest in 1968 and 1976 (over 20 representatives in 5 sports).

- **Recent Trends**: In the last three Olympics, India sent over 100 representatives competing in more than 13 sports.

- **Medal Tally**: India won over 5 medals in the 2012 London and 2021 Tokyo Olympics.

- **Field Hockey Success**: Indian men's field hockey team won medals in every Olympic edition from 1928 (Amsterdam) to 1980 (Moscow), and again a bronze in 2021 Tokyo. 

### What is the gender representation?



```{r fig.height = 8, fig.width = 10}

year_gender_n <- ind_olympics |>
    filter(season == "Summer") |>
    select(id, name, sex, year, sport, city) |>
    distinct() |>
    group_by(year, sex) |>
    summarize(representation = n(),
             #medals = sum(!is.na(medal)),
              game = paste(year, city)) |>
    distinct() |>
    mutate(sex = ifelse(sex == "M", "men", "women")) |>
    pivot_wider(
        names_from = sex,
        values_from = representation
    ) |>
    mutate(across(c(men, women), ~ifelse(is.na(.x), 0, .x)),
           total = men + women)

plot2_df <- year_gender_n |>
    rbind(tokyo_df |> summarize(
        year = year,
        game = game,
        men = sum(men), women = sum(women),
        total = sum(total))) |>
    rbind(paris24_representation |> summarize(
        year = year,
        game = game,
        men = sum(men), women = sum(women),
        total = sum(athletes))) |>
    distinct() |>
    mutate(prop_men = men/total,
           prop_women = women/total)

plot2 <- ggplot(plot2_df, aes(x = year))+
    geom_line(aes(y = prop_men), color = "orange") +
    geom_ribbon(aes(ymin = 0.5,ymax = prop_men), fill = "orange", alpha = 0.5)+
    geom_line(aes(y = prop_women), color = "coral") +
    geom_ribbon(aes(ymin = prop_women,ymax = 0.5), fill = "coral", alpha = 0.5) +
    geom_vline(xintercept = 1947, color  = "#06038D", linetype = 2) + #India independence
    scale_x_continuous(
        breaks = sort(unique(plot2_df$year)),
        labels = sort(unique(plot2_df$game))
    ) +
    labs(
        x = "",
        y = "Representation",
        title = paste0("<span style='color:darkorange2;'>Men</span> and <span style='color:coral4;'>Women</span> representatives <br>in the ", "<img src = '", logo_path,"' height = 18> Summer Olympics Contingent"),
         caption = "Source: RGriffin Olympic Dataset for 1900-2016, and Wikipedia for 2021 and 2024.\nTotal includes representatives who participated, doesn't include representatives on reserve for 2024."
    ) +
    theme_minimal(30)+
    annotate(
        geom = "text",
        x = 1988,
        y = 0.9,
        label = "Men",
        color = "darkorange2",
        size = 10
    )+
    annotate(
        geom = "text",
        x = 1988,
        y = 0.1,
        label = "Women",
        color = "coral4",
        size = 10
    )+
    annotate(
        geom = "text",
        x = 1896,
        y = -0.075,
        label = "Total",
        color = "gray40",
        size = 10
    )+
     annotate(
    geom = "label", 
    x = 1945, 
    y = 0.5,
    label = "Became Independent",
    color = "#06038D",
    size = 8
  ) +
    geom_text(data = plot1_df %>% select(year, total) %>% distinct(),
              aes(x = year, y = -0.075, label = total),
              size = 8,
              angle = 8)+
    scale_y_continuous(expand = c(0.1,0),
                       labels = scales::percent,
                       breaks = seq(0,1,0.1))+
    theme(
        text = element_text(family = "Open Sans"),
        plot.title = ggtext::element_markdown(hjust =0.5, face = "bold", lineheight = 0.25),
        axis.text.x = element_text(angle = 60, hjust = 0.95, color = "gray40",
                                   size = 24),
        plot.caption = element_text(color = "gray40", size = 24,                            lineheight = 0.5),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(color = "azure2", linewidth = 0.2),
        legend.box.spacing = margin(0.1)
    )
    
plot2
#ggsave("men_women_olympics.jpeg",plot2, height = 6, width = 9)
```

- **Male-Dominated Contingent**: Male representatives dominated India's Olympic contingent until the 1976 Montreal Games.

- **Increase in Female Representation**: Since 1976, over 15% of the contingent has consistently been women.

- **Recent Trend**: In the last three Olympic editions, more than 40% of the Indian contingent was women.

### What sports do we compete in?


```{r fig.height = 10, fig.width = 10}
plot1 <- ggplot(plot1_df) +
    #geom_vline(xintercept = "1948 London", color = "#06038D", linetype = 2)+
    geom_point( aes(x = game, y = sport, color = representation, size = representation),
                alpha = 0.6) +
    #scale_size_manual(values = c(1.5,2,4,5,6))+
    #scale_color_brewer(palette = "BuPu")+
    scale_color_manual(values = c("black", "#DF0024", "#0085C7", "#009F3D", "#F4C300"))+
  
    geom_text(data = plot1_df %>% select(game, total) %>% distinct(),
              aes(x = game, y = 1, label = total),
              size = 7,
              angle = 5)+
    scale_y_discrete(limits = c("Total", sort(unique(plot1_df$sport), decreasing = TRUE)))+
    labs(x = "",
         y = "",
         title = paste0("<img src = '", logo_path,"' height = 18> Summer Olympics Contingent by Sport"),
         color = "",
         size = "",
         caption = "Source: RGriffin Olympic Dataset for 1900-2016, and Wikipedia for 2021 and 2024.\nTotal includes representatives who participated, doesn't include representatives on reserve for 2024") +
  #    annotate(
  #   geom = "label", 
  #   x = "1948 London", 
  #   y = "Archery",
  #   label = "Became Independent",
  #   color = "#06038D",
  #   size = 8
  # )+
    theme_minimal(30)+
    theme(
        text = element_text(family = "Open Sans"),
        plot.title = ggtext::element_markdown(hjust =0.5, face = "bold"),
        axis.text.x = element_text(angle = 60, hjust = 0.95, color = "gray40",
                                   size = 24),
        plot.caption = element_text(color = "gray40", size = 24,
                                    lineheight = 0.5, face = "italic"),
        panel.grid.major.y = element_blank(),
        legend.box.spacing = margin(0.1)
    )

plot1
#ggsave("representation.jpeg", plot1, height = 6.5, width = 8)
```

- **Consistent Participation in Athletics**: India has participated in athletics in all Olympic editions, with the contingent size increasing notably since the 1996 Atlanta Games.

- **Field Hockey**: Field hockey has consistently been a major sport in India's Olympic contingent.

- **Growing Representation in Specific Sports**: Archery, badminton, boxing, shooting, and wrestling have seen significant representation in recent years. Table tennis, tennis, and weightlifting also have notable participation.

- **Limited Participation in Certain Sports**: India has only participated once in basketball and fencing, and four times in football and thrice in cycling.

- **Niche Sports**: There has been a small yet noticeable increase in Indian representation in niche sports such as equestrianism, judo, rowing, and sailing.

<!-- # Timeline -->

```{r}
# c(1900 = "First athlete to represent any Asian country, though he was born to British parents in Calculta (India)",
#   1920 = "First native athletes participated",
#   1924 = "First women participated in Tennis, born to British parents in India",
#   1928 = "Hockey medal streak begins; India continues to win until 1972 Munich (7 gold, 1 silver, 2 bronze)",
#   1932 = "2 representatives in Mixed Painting",
#   1936 = "First time participating in weight-lifting and wrestling"
# )
  
```
